\documentclass[11pt,a4paper]{article}
\usepackage[margin=0.75in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}

% Hyperref setup for clean links
\hypersetup{
    colorlinks=false,
    pdfborder={0 0 0},
}

% Remove page numbers
\pagestyle{empty}

% Section formatting
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{10pt}{5pt}

% Subsection formatting
\titleformat{\subsection}{\normalsize\bfseries}{}{0em}{}
\titlespacing*{\subsection}{0pt}{8pt}{3pt}

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{#1}}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\begin{document}

% Header
\begin{center}
    {\huge \textbf{Chou Cheng Lei (Eli)}}\\
    \vspace{5pt}
    (886) 9011-362-56 | chenglei.chou@email.com | github.com/memoriaXII | linkedin.com/in/cheng-lei
\end{center}

\vspace{5pt}

% Education Section
\section{Education}
\textbf{James Cook University}, Brisbane, Australia \hfill \textit{2015 -- 2019}\\
- Bachelor of Information Technology - Computing and Networking\\

\vspace{0pt}

% Skills Section - Enhanced for 2025 Blockchain Frontend

\section{Skills}
\textbf{Languages:} JavaScript, TypeScript, Rust, Solidity\\
\textbf{Frontend:} React, Next.js, Vue.js, HTML/CSS, Tailwind CSS\\
\textbf{Backend:} Node.js, MongoDB, PostgreSQL\\
\textbf{Blockchain:} Web3.js, Ethers.js, Wagmi, Viem, Hardhat, Foundry\\
\textbf{Tools \& Infrastructure:} Git, Docker, AWS, Jest
\vspace{0pt}

% Working Experience Section
\section{Working Experience}
\subsection{Founding Blockchain Fullstack Engineer, Aerix Protocol, Singapore \hfill \textit{Feb.2025 -- Present}}
\begin{itemize}[leftmargin=*, itemsep=1pt, parsep=0pt]
    \resumeItem{Architected and engineered Stratus Exchange from 0-to-1, achieving \$939K+ volume and 6,689+ users within 8 weeks as sole technical lead.}
    \resumeItem{Designed advanced routing algorithms with intelligent path splitting across 15+ liquidity sources, optimizing price impact and minimizing slippage for traders.}
    \resumeItem{Built proprietary quote aggregation engine processing 56K+ swaps with 99.9\% success rate and supporting 200+ token pairs across multiple EVM chains.}
    \resumeItem{Optimized gas estimation algorithms and transaction batching, reducing user transaction costs by 40\% through
intelligent route optimization.}
    \resumeItem{Designed novel intent-to-execution architecture with off-chain order book, solver network, and arbitrary fulfillment logic supporting cross-chain settlement.}
    \resumeItem{Engineered Permit2-based order system with pre/post-execution hooks, enabling programmable trade settlement and MEV-resistant batch fulfillment.}
    \resumeItem{Built high-performance order processing pipeline with PostgreSQL clustering, Redis caching, and WebSocket streaming, handling fills with sub-100ms execution latency.}

\end{itemize}

\subsection{Lead Blockchain Software Engineer, zkLink Protocol, Singapore \hfill \textit{Apr.2024 -- Jan.2025}}
\begin{itemize}[leftmargin=*, itemsep=1pt, parsep=0pt]
    \resumeItem{Led cross-functional development coordination across 14+ team members spanning smart contracts, backend infrastructure, and frontend teams, ensuring synchronized delivery and technical alignment.}
    \resumeItem{Spearheaded NovaSwap concentrated liquidity DEX from 0-to-1, leading team coordination for Uniswap V3-style pools achieving \$4M+ TVL across Layer 2 assets.}
    \resumeItem{Designed sophisticated multi-asset liquidity vault (ALP) architecture unifying spot swaps, market making, and leveraged trading through single liquidity source with dynamic risk management.}
    \resumeItem{Built comprehensive yield optimization system aggregating rewards from EigenLayer restaking, LRT protocols, and zkLink incentives, delivering institutional-grade returns for liquidity providers.}
    \resumeItem{Developed AGX perpetual trading protocol to production-ready state, implementing unified multi-asset liquidity pool (ALP), oracle-based pricing, and zero-slippage execution with automated liquidation and funding rate mechanisms.}
    \resumeItem{Built sophisticated trading interface for multi-asset liquidity vault (ALP), managing cross-team dependencies and technical specifications across 3 development streams for on-time delivery.}
    \resumeItem{Built sophisticated frontend interfaces for multi-asset liquidity vault (ALP) supporting stablecoins, ETH, WBTC, and LRTs, enabling unified swap and leveraged trading functionality.}
    \resumeItem{Implemented Pyth Network oracle integration and coordinated liquidation engine development for MEV-resistant execution across perpetual positions.}
    \resumeItem{Developed comprehensive GraphQL indexing infrastructure using The Graph for LP positions, trading analytics, and real-time position tracking across both protocols.}

\end{itemize}

\subsection{Blockchain Software Engineer, OpenEden, Singapore \hfill \textit{Apr.2023 -- Mar.2024}}
\begin{itemize}[leftmargin=*, itemsep=1pt, parsep=0pt]
    \resumeItem{Built comprehensive DApp frontend supporting OpenEden protocol's growth to \$150M+ TVL, serving 130+ institutional clients across Binance Labs-backed tokenized US Treasury Bills platform.}
    \resumeItem{Developed cross-chain vault interfaces for Ethereum, Arbitrum, and XRP Ledger, enabling seamless interaction with Moody's "A"-rated TBILL tokens and automated yield distribution systems.}
    \resumeItem{Architected modular component library integrating Wagmi, Viem, Ethers.js, and Typechain for enterprise-grade KYC/AML workflows and institutional treasury management interfaces.}
    \resumeItem{Led frontend development for River Finance, implementing DFS automation with proxy account (DS-Proxy) interfaces for leverage vault management and automated rebalancing mechanisms.}
    \resumeItem{Implemented sophisticated FlashLoan integration and staking token incentive systems with comptroller-based point accumulation, contributing to institutional access for RWA-backed leveraged positions.}
\end{itemize}

\subsection{Blockchain Frontend Engineer, KONOMI Network \& So-Col, Singapore \hfill \textit{Apr.2022 -- Apr.2023}}
\begin{itemize}[leftmargin=*, itemsep=1pt, parsep=0pt]
    \resumeItem{Built comprehensive P2P lending protocol frontend for KONOMI Network enabling user-controlled yield farming with custom pool creation, interest rate setting, and collateral management on Polkadot ecosystem.}
    \resumeItem{Developed cross-chain asset management interface integrating custom Konomi Oracle for accurate price feeds across BSC, Ethereum, and Polkadot networks supporting minority currency lending markets.}
    \resumeItem{Engineered real-time WebSocket and Server Side Event systems processing 10K+ concurrent users for live trading data, liquidation alerts, and governance proposal updates.}
    \resumeItem{Contributed to So-Col Web3 social platform development, implementing NFT-gated community features and creator monetization tools for \$4.5M DWF Labs-backed platform serving 300+ creators.}
    \resumeItem{Applied Agile methodologies using JIRA, Jenkins, and GitHub for continuous integration across both protocols, maintaining 95\% test coverage with Jest and comprehensive Solidity unit testing.}
\end{itemize}

\subsection{Software Engineer, DBS Bank, Taipei, Taiwan \hfill \textit{Mar.2021 -- Mar.2022}}
\begin{itemize}[leftmargin=*, itemsep=1pt, parsep=0pt]
    \resumeItem{Selected through competitive DBS Hack2Hire Taiwan program, joining DBS Taiwan engineering team to develop enterprise-grade digital banking and credit card solutions serving millions of customers.}
    \resumeItem{Implemented critical hot-fixes and new features for credit card and lending platforms, collaborating with Singapore-based engineering teams on mission-critical financial services.}
    \resumeItem{Optimized Digital Taiwan application performance achieving 25\% system improvement and 40\% crash rate reduction through advanced debugging and code refactoring techniques.}
    \resumeItem{Built responsive React-based interfaces with TypeScript, Redux-Saga state management, and comprehensive Jest testing frameworks meeting financial industry compliance standards.}
    \resumeItem{Collaborated across Singapore-Taiwan engineering teams using Agile methodologies, JIRA workflow management, and Jenkins CI/CD pipelines for seamless cross-border development coordination.}
\end{itemize}

\subsection{Frontend Developer, Eatme Internet Co, Ltd (Eatgether), Taiwan \hfill \textit{Mar.2020 -- Nov.2020}}
\begin{itemize}[leftmargin=*, itemsep=1pt, parsep=0pt]
    \resumeItem{Developed and maintained Taiwan's largest social meetup platform serving 1M+ users, enabling face-to-face social connections through 10,000+ hosted gatherings with zero safety incidents.}
    \resumeItem{Built comprehensive admin dashboard for sales department optimizing advertisement implementations and essential platform controls, supporting 290\% monthly revenue growth.}
    \resumeItem{Implemented real-time features using Vue.js, React, WebSocket, and SASS, integrating AWS Lambda and S3 for scalable cloud infrastructure supporting rapid user growth.}
    \resumeItem{Collaborated with backend teams on platform development during company's pre-Series A funding round, contributing to expansion plans targeting East Asia's largest meetup platform.}
\end{itemize}

\vspace{10pt}

% Awards & Certifications
\section{Certifications}
\textbf{DBS Bank SRE Advanced Practitioner Certification} \hfill \textit{Oct.2021}\\
Site reliability engineering and production infrastructure management\\
\textbf{DBS Bank Application Security Titan Bronze Level} \hfill \textit{Mar.2021}\\
Advanced application security practices and vulnerability assessment\\

\vspace{0pt}

% Selected Projects Section
\section{Selected Projects}
\textbf{create-web3-turbo - Web3 Development Monorepo Template} \hfill \textit{Oct.2022}\\
\textit{TypeScript, Next.js, Turborepo, Hardhat | github.com/memoriaXII/create-web3-turbo}
\begin{itemize}[leftmargin=*, itemsep=1pt, parsep=0pt]
    \resumeItem{Architected production-ready Web3 monorepo template achieving 144+ GitHub stars and 23+ forks, serving as foundation for multiple DeFi projects.}
    \resumeItem{Built comprehensive development stack integrating Next.js 14, WAGMI hooks, RainbowKit, Hardhat, and Typechain with advanced CI/CD workflows.}
    \resumeItem{Designed modular architecture supporting smart contract development, frontend integration, and shared component libraries with Docker containerization.}
\end{itemize}
\textbf{SkyArk Chronicles - AAA Blockchain Gaming Platform} \hfill \textit{Feb.2022 -- Nov.2022}\\
\textit{React, TypeScript, Web3.js, Solidity — Binance Labs-backed, \$15M funding}
\begin{itemize}[leftmargin=*, itemsep=1pt, parsep=0pt]
    \resumeItem{Contributed to Singapore's first AAA blockchain gaming studio backed by Binance Labs, developing DeFi protocol DApps for fantasy JRPG with interoperable NFTs and play-and-own mechanics.}
    \resumeItem{Built sophisticated GameFi interfaces utilizing Solidity smart contracts with comprehensive unit testing and SDK integration, supporting SkyEngine's blockchain-as-a-service platform.}
    \resumeItem{Implemented real-time WebSocket and Server-Side Event systems for multiplayer gaming features, NFT marketplace functionality, and efficient data communication across the SkyArk Chronicles trilogy.}
    \resumeItem{Developed frontend solutions using JavaScript, TypeScript, React, Redux-Toolkit, and Jest, integrating Web3.js and Hardhat for seamless Ethereum blockchain interactions.}
    \resumeItem{Applied Agile methodologies using JIRA, Jenkins, Git, and Docker for streamlined development processes, ensuring high-quality deliverables for this venture-backed gaming ecosystem.}
\end{itemize}

\end{document}